\huge Modeling Intervention Strategies for United States TB Control

### 2013-08-27 in_progress/presentations/poster/reuMHC2013NoSIRIntro.tex
added bracket to caption
fixed other graph and finalized poster
fixed poster

      \begin{block}{Intervention Analysis}
        %\vspace{-1.6em}
        \begin{figure}[h]
          \begin{minipage}[c]{0.6\textwidth}
            \includegraphics[height=0.7\textwidth,width=\textwidth]{redEnLTBIIncGrouped}
          \end{minipage}
          \hspace{0.5em}
          \begin{minipage}[c]{0.35\textwidth}
            \caption{Incidence/million in USB, FB, and total populations,
                     given 0\%, 50\%, 75\%, or 100\% treatment of incoming
                     LTBI}
          \end{minipage}
          \label{fig:redEnLTBI_incidence}
        \end{figure}
        \begin{figure}[h]
          \begin{minipage}[c]{0.6\textwidth}
            \includegraphics[height=0.7\textwidth,width=\textwidth]{incLTBItrmtIncGrouped}
          \end{minipage}
          \hspace{0.5em}
          \begin{minipage}[c]{0.35\textwidth}
            \caption{Incidence/million in USB, FB, and total populations,
                     given 0\%, 100\%, or 300\% LTBI treatment increase}
          \end{minipage}
          \label{fig:incLTBItrmt_incidence}
        \end{figure}
      \end{block}
      \begin{block}{Economic Modeling}
        \begin{itemize}
          \item Tracks treatment costs for various disease states
          \item Estimates implementation cost of intervention
          \item Mean Active TB Treatment Cost: \$14,014.90

        \end{itemize}
        \vspace{.5em}
        %\begin{columns}[T]
          %\begin{column}{.66\textwidth}
            \begin{figure}[h]

              \begin{minipage}[c]{0.6\textwidth}
                \includegraphics[height=0.7\textwidth,width=\textwidth]{costAvertedRedEnLTBI}
              \end{minipage}
              \hspace{0.5em}
              \begin{minipage}[c]{0.35\textwidth}
                   \caption{Cumulative US HCS savings from averted Active TB 
                                treatment costs given intervention magnitude.  
                                Does not include savings from averted LTBI treatment costs.  
%                \caption{Cumulative implementation costs, US HCS savings, and net
%                       US costs of LTBI arrival cure rates. Cost/case cured was
%                       \$600, \$800, and \$1000 for 50\%, 75\%, and 100\%
%                       cured}
              \end{minipage}
              \label{fig:redEnLTBI_costs} 
            \end{figure}
          %\end{column}
          %\begin{column}{.26\textwidth}
            % Base HCS Costs:
            % \begin{description}
            %   \item[Active TB:]\hfill \\ 
            %     \$14,014.90
            %   \item[LTBI:]\hfill \\ 
            %     \$403.45
            % \end{description}
          %\end{column}
        %\end{columns}
      \end{block}
    \end{column}

@@

      \begin{block}{Stochastic Models as a Measure of Variability}
        %\begin{columns}[T]
          %\begin{column}{.45\textwidth}
            %\begin{figure}[h]
              %\begin{center}
                %\includegraphics[height=0.5\textwidth,width=\textwidth]{IN0dist}
              %\end{center}
              %\caption{USB Incidence (\texttt{c++}) with fitted Normal curve ($\mu = 0.233196, \sigma = 0.016534$)}
              %\label{fig:IN0dist}
            %\end{figure}
          %\end{column}
          %\begin{column}{.45\textwidth}
            %\begin{figure}[h]
              %\begin{center}
                %\includegraphics[height=0.5\textwidth,width=\textwidth]{IN1dist}
              %\end{center}
              %\caption{FB Incidence (\texttt{c++}) with fitted Normal curve ($\mu = 98.6087, \sigma = 0.525294$)}
              %\label{fig:IN1dist}
            %\end{figure}
          %\end{column}
        %\end{columns}
        \begin{figure}[h]
          \begin{center}
            \includegraphics[width=0.45\textwidth]{IN0dist}
            \hspace{0.8em}
            \includegraphics[width=0.45\textwidth]{IN1dist}
          \end{center}
          \caption{USB and FB Incidence (\texttt{c++}) with fitted Normal curves (USB: $\mu = 0.233, \sigma = 0.016534$, FB: $\mu = 98.6, \sigma = 0.525294$)}
          \label{fig:INdist}
        \end{figure}
              %\caption{FB Incidence (\texttt{c++}) with fitted Normal curve ($\mu = 98.6087, \sigma = 0.525294$)}
              %\label{fig:IN1dist}
      \end{block}

      \begin{block}{Summary}
        \begin{itemize}
          \item LTBI dominates US TB dynamics
          \item Reducing FB LTBI most cost effective
          \item Agent-based models effective for evaluating robustness
        \end{itemize}
      \end{block}
      %\vspace{.9em}
      \begin{block}{References \& Acknowledgments}
        This research was supported via an NSF REU grant. 
        \small{[1] Hill, A. N., Becerra, J. E., \& Castro, K. G. (2012). Modelling
          tuberculosis trends in the USA. Epidemiology and infection, 140(10),
          1862.}
      \end{block}

>>>>

      \begin{block}{Intervention Analysis}
        %\vspace{-1.6em}
        \begin{figure}[h]
          \begin{minipage}[c]{0.6\textwidth}
            \includegraphics[height=0.7\textwidth,width=\textwidth]{redEnLTBIIncGrouped}
          \end{minipage}
          \hspace{0.5em}
          \begin{minipage}[c]{0.35\textwidth}
            \caption{Incidence/million in USB, FB, and total populations,
                     given 0\%, 50\%, 75\%, or 100\% cure rate of incoming
                     LTBI}
          \end{minipage}
          \label{fig:redEnLTBI_incidence}
        \end{figure}
        \begin{figure}[h]
          \begin{minipage}[c]{0.6\textwidth}
            \includegraphics[height=0.7\textwidth,width=\textwidth]{incLTBItrmtIncGrouped}
          \end{minipage}
          \hspace{0.5em}
          \begin{minipage}[c]{0.35\textwidth}
            \caption{Incidence/million in USB, FB, and total populations,
                     given 0\%, 100\%, or 300\% LTBI treatment increase}
          \end{minipage}
          \label{fig:incLTBItrmt_incidence}
        \end{figure}
      \end{block}
      \begin{block}{Economic Modeling}
        \begin{itemize}
          \item Tracks treatment costs for various disease states
          \item Estimates implementation cost of intervention
          \item Assumed Mean Active TB Treatment Cost: \$14,015
        \end{itemize}
        \vspace{.5em}
        %\begin{columns}[T]
          %\begin{column}{.66\textwidth}
            \begin{figure}[h]

              \begin{minipage}[c]{0.6\textwidth}
                \includegraphics[height=0.7\textwidth,width=\textwidth]{costAvertedRedEnLTBI}
              \end{minipage}
              \hspace{0.5em}
              \begin{minipage}[c]{0.35\textwidth}
                   \caption{Cumulative US HCS savings from averted Active TB 
                                treatment costs given intervention magnitude.  
                                Does not include savings from averted LTBI treatment costs.}  
%                \caption{Cumulative implementation costs, US HCS savings, and net
%                       US costs of LTBI arrival cure rates. Cost/case cured was
%                       \$600, \$800, and \$1000 for 50\%, 75\%, and 100\%
%                       cured}
              \end{minipage}
              \label{fig:redEnLTBI_costs} 
            \end{figure}
          %\end{column}
          %\begin{column}{.26\textwidth}
            % Base HCS Costs:
            % \begin{description}
            %   \item[Active TB:]\hfill \\ 
            %     \$14,014.90
            %   \item[LTBI:]\hfill \\ 
            %     \$403.45
            % \end{description}
          %\end{column}
        %\end{columns}
      \end{block}
    \end{column}

@@

      \vspace{.33em}
      \begin{block}{Stochastic Models as a Measure of Variability}
        %\begin{columns}[T]
          %\begin{column}{.45\textwidth}
            %\begin{figure}[h]
              %\begin{center}
                %\includegraphics[height=0.5\textwidth,width=\textwidth]{IN0dist}
              %\end{center}
              %\caption{USB Incidence (\texttt{c++}) with fitted Normal curve ($\mu = 0.233196, \sigma = 0.016534$)}
              %\label{fig:IN0dist}
            %\end{figure}
          %\end{column}
          %\begin{column}{.45\textwidth}
            %\begin{figure}[h]
              %\begin{center}
                %\includegraphics[height=0.5\textwidth,width=\textwidth]{IN1dist}
              %\end{center}
              %\caption{FB Incidence (\texttt{c++}) with fitted Normal curve ($\mu = 98.6087, \sigma = 0.525294$)}
              %\label{fig:IN1dist}
            %\end{figure}
          %\end{column}
        %\end{columns}
        \begin{figure}[h]
          \begin{center}
            \includegraphics[width=0.45\textwidth]{IN0dist}
            \hspace{0.8em}
            \includegraphics[width=0.45\textwidth]{IN1dist}
          \end{center}
          \caption{USB and FB Incidence (\texttt{c++}) with fitted Normal curves (USB: $\mu = 0.233, \sigma = 0.016534$, FB: $\mu = 98.6, \sigma = 0.525294$)}
          \label{fig:INdist}
        \end{figure}
              %\caption{FB Incidence (\texttt{c++}) with fitted Normal curve ($\mu = 98.6087, \sigma = 0.525294$)}
              %\label{fig:IN1dist}
      \end{block}

      \vspace{.33em}
      \begin{block}{Summary}
        \begin{itemize}
          \item LTBI dominates US TB dynamics
          \item Reducing FB LTBI most cost effective
          \item Agent-based models effective for evaluating robustness
        \end{itemize}
      \end{block}
      \vspace{.33em}
      \begin{block}{References \& Acknowledgments}
        This research was supported via an NSF REU grant. 
        \small{[1] Hill, A. N., Becerra, J. E., \& Castro, K. G. (2012). Modelling
          tuberculosis trends in the USA. Epidemiology and infection, 140(10),
          1862.}
      \end{block}
